### 2015-07-06 narrative/intro.tex
edits
changes to make this more readable.

{\em The purpose of computing is insight, not numbers}~\cite{Hamming:book}.
Richard Hamming's remark, made over 50 years ago at the dawning of the age of
large scale scientific computation, is even more relevant today as we prepare
for scientific simulation at exascale. 
The central objective of this proposal, ``minimizing the time knowledge'' from 
scientific computing, aligns perfectly with this sentiment. 
%Hamming was a pioneer in the fields of coding theory, scientific computing and 
%information theory who would instantly sympathize with the central objective of 
%this proposal--minimizing the time to knowledge.

@@

Take for example the latest use case for the XGC1 simulation from C. S. Chang (PPPL), who is one of the largest users of Leadership Class Facilities (over 300M hours at ALCF, NERSC, and OLCF). They launched a series of simulations, planning to produce 100~PB of data over 10 days of total runtime on the Titan system. An expert team was assembled from the user group, the middleware I/O team to help with the application I/O (ADIOS), the local experts of the Lustre file-system and the tape archival system (HPSS). Due to physical resource limitations, the simulation was restricted to write about 10~PB initially. However, once the time to write and read, together with the financial cost to archive this much data were more fully explored, this plan was again signficantly reduced. At each stage, the particular expert knowledge regarding the lustre file system and the archival tape storage were not known to the user team. As these particulars were realized, significant modifications in the plans were made. Eventually, the user was forced to make very hard decisions in reducing the desired 100~PB over a 10-day run to a mere 5~PB of data. A maximum of 2~PB would be on disk, and the rest would be archived.

This forced the team to carefully scrutinize the large amount of data to be generated and save only the very most important pieces. Further, they had to break this greatly reduced data into two categories: first data they thought they would need to access while the simulation was running or shortly thereafter, and second data they would need after the simulation was finished. The former category would be stored on disk, and the later would be archived. Additionally, they needed to figure out how to efficiently retrive these different categories of data for post-processing, analysis and visualization.

@@

\subsection{Storage System Perspective}
\label{subsec:storage-perspective}
From the perspective of the storage system, it is necessary to manage the data from
a given user request amongst all of the requests from all users, and try to optimize the
entire system accordingly. Today the problem is that when a user writes there is a
tremendous amount of interference from other users on the system who may be
writing or reading at the same time. By requiring a certain quality
of service the {\bf {\color {red} system must potentially lock out users with lower currency
they want to place in the reading or writing of their data}}. The storage
system must also automatically move data from one tier of the storage to
another, without affecting the quality of service that was offered at request
time. The storage system must be able to organize
data amongst all of the tiers of storage in a known, consistent way.

>>>>

{\em The purpose of computing is insight, not numbers}~\cite{Hamming:book}.
Richard Hamming's remark, made over 50 years ago at the dawning of the age of
large scale scientific computation, is even more relevant today as we prepare
for scientific simulation at exascale. 
The central objective of this proposal, ``minimizing the time to knowledge'' from 
scientific computing, aligns perfectly with this sentiment. 
%Hamming was a pioneer in the fields of coding theory, scientific computing and 
%information theory who would instantly sympathize with the central objective of 
%this proposal--minimizing the time to knowledge.

@@

Take for example the latest use case for the XGC1~\cite{chang2006integrated} simulation from C. S. Chang (PPPL), who is one of the largest users of Leadership Class Facilities (over 300M hours at ALCF, NERSC, and OLCF). They launched a series of simulations, planning to produce 100~PB of data over 10 days of total runtime on the Titan system. An expert team was assembled from the user group, the middleware I/O team to help with the application I/O (ADIOS), the local experts of the Lustre file-system and the tape archival system (HPSS). Due to physical resource limitations, the simulation was restricted to write about 10~PB initially. However, once the time to write and read, together with the financial cost to archive this much data were more fully explored, this plan was again significantly reduced. At each stage, the particular expert knowledge regarding the lustre file system and the archival tape storage were not known to the user team. As these particulars were realized, significant modifications in the plans were made. Eventually, the user was forced to make very hard decisions in reducing the desired 100~PB over a 10-day run to a mere 5~PB of data. A maximum of 2~PB would be on disk, and the rest would be archived.

This forced the team to carefully scrutinize the large amount of data to be generated and save only the very most important pieces. Further, they had to break this greatly reduced data into two categories: first data they thought they would need to access while the simulation was running or shortly thereafter, and second data they would need after the simulation was finished. The former category would be stored on disk, and the later would be archived. Additionally, they needed to figure out how to efficiently retrieve these different categories of data for post-processing, analysis and visualization.

@@

\subsection{Storage System Perspective}
\label{subsec:storage-perspective}
From the perspective of the storage system, it is necessary to manage the data from
a given user request amongst all of the requests from all users, and try to optimize the
entire system accordingly. Today the problem is that when a user writes there is a
tremendous amount of interference from other users on the system who may be
writing or reading at the same time. By requiring a certain quality
of service the {\bf  system must potentially lock out users with lower currency
they want to place in the reading or writing of their data}. The storage
system must also automatically move data from one tier of the storage to
another, without affecting the quality of service that was offered at request
time. The storage system must be able to organize
data amongst all of the tiers of storage in a known, consistent way.

### 2015-07-06 narrative/proposed-work.tex
changes to make this more readable.

\underline{Principle 1:} A knowledge-centric system , let user knowledge  to
define data policies. Today Storage System and I/O layers are written in a
stove-pipe fashion, and quite often do not allow optimizations to take place.
We propose to re-design the layer in a highly integrated fashion where user
will place their intentions into the system and actions will dynamically and
statically take place to optimize for both the system and for individual
requests.

\underline{Principle 2}: Predictable Performance in the SSIO layer needs to be
established so more science can be done on the exascale systems. Without
predictable performance, the I/O layer performance must be guessed by the
users, which quite often mean that science is not performed well.

\underline{Principle 3:} In a data-centric SSIO system, we need user goals to
define the data policies. We introduce data-driven SSIO optimizations by
enabling users to define data manipulations (re-organizations) at a high level
and then we express policy goals by associating intentions (hints) with data;
e.g. ``this data at this level should be accessible within 100 seconds in the
next three months.'' These high level specifications of desired results will be
used in our system for data migration and eviction policies.

>>>>

\underline{Principle 1:} {\bf A knowledge-centric system}, let user knowledge  to
define data policies. Today Storage System and I/O layers are written in a
stove-pipe fashion, and quite often do not allow optimizations to take place.
We propose to re-design the layer in a highly integrated fashion where user
will place their intentions into the system and actions will dynamically and
statically take place to optimize for both the system and for individual
requests.

\underline{Principle 2}: {\bf Predictable Performance in the SSIO layer} needs to be
established so more science can be done on the exascale systems. Without
predictable performance, the I/O layer performance must be guessed by the
users, which quite often mean that science is not performed well.

\underline{Principle 3:} {\bf Users goals define data policies} In a data-centric SSIO system. 
We introduce data-driven SSIO optimizations by
enabling users to define data manipulations (re-organizations) at a high level
and then we express policy goals by associating intentions (hints) with data;
e.g. ``this data at this level should be accessible within 100 seconds in the
next three months.'' These high level specifications of desired results will be
used in our system for data migration and eviction policies.
